Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-05-28 tex/VHzQ.tex
data data/WSA_VSA/BestVSA_magnitudes_v201* update

\maketitle
\begin{abstract}
In this paper, we, for the first time since the discovery of $z\geq5$
quasars, assemble all spectroscopically confirmed very high redshift
quasars in one catalogue.  In particular we present the near
($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
photometric variability in the near-infrared that might be expected
from Super-Eddington accretion and find {\it blah}.  We present a
comprehensive series of colour-redshift and colour-colour plots and
make inferences into the hot dust properties of the very high-redshift
quasar population. Extrapolating the known quasar luminosity function
we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
current datasets have been discovered. 
All the data, analysis codes and plots used and generated here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

>>>>

\maketitle
\begin{abstract}
%For the first time since the discovery of $z\geq5.00$ quasars, 
%In this paper, 
We assemble a catalogue of 463 
spectroscopically confirmed very high ($z\geq5.00$) redshift 
quasars %in one catalogue.  
%In particular we present the near
and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties. 
%of all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for
photometric variability in the near-infrared that might be expected
from super-Eddington accretion and find {\it blah}.  
%%
% We present a comprehensive series of colour-redshift and colour-colour plots and make inferences into the hot dust properties of the very high-redshift quasar population. aq
Extrapolating the known quasar luminosity function
we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
current datasets have been discovered. 
All the data, analysis codes and plots used and generated here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:

%% I have also checked for QSOs with large differences in magnitude. At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean. In fact initially there were 100 QSO/filter combinations. However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0. and >5 average flux error. This removed 80-90\%. I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either. This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:

The two with large differences are:

SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and

SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
